Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-12 paper/paper.tex
fewer referee isues

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric \lya\ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the 
velocities found by our models, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

\begin{keywords}
Methods: data analysis - numerical 
\end{keywords}

@@

Primordial galaxies have not been detected yet. 
However, dwarf star forming galaxies with a low metallicity content
are seen as templates to understand the early galaxy evolution process. 
Over fifty years ago \citep{PartridgePeebles} it was realized that
young galaxies could be detected through a strong \lya\ line
emission.

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the \lya\ emission line provides confirmation of
the distance of a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
\lya\ emission.
A careful clustering analysis of LAEs can also yield clues about their link
to dark matter halos \cite{2016ApJ...828....5M}.

The \lya\ emission line is not exclusive of distant galaxies. 
There are local Universe surveys that target \lya\ emission in nearby
dwarf star forming galaxies.
The study of nearby LAE samples has allowed the study of other
indicators that might be more difficult to obtain for distant galaxies
such as morphology, dust attenuation, neutral hydrogen contents and
ionization state. (see \citep{Hayes15} and references therein for a review.)

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models

>>>>

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric \lya\ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated
baryonic mass.     
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work suggests the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the 
velocities found by our models, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

\begin{keywords}
galaxies: dwarf --- galaxies: individual:\tol\ --- radiative transfer --- Methods: numerical 
\end{keywords}

@@

Primordial galaxies have not been detected yet. 
However, dwarf star forming galaxies with a low metallicity content
are seen as templates to understand the early galaxy evolution process. 
Over fifty years ago it was realized that young galaxies could be
detected through a strong \lya\ line emission \citep{PartridgePeebles}.

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the \lya\ emission line provides confirmation of
the distance to a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
\lya\ emission.
A careful clustering analysis of LAEs can also yield clues about their link
to dark matter halos
\citep{2004AJ....128.2073H,2007ApJ...671..278G,2007ApJ...668...15K,2008MNRAS.391.1589O,2010MNRAS.409..184P,2013MNRAS.431.1777G,2016ApJ...828....5M}.

The \lya\ emission line is not exclusive of distant galaxies. 
There are local Universe surveys that target \lya\ emission in nearby
dwarf star forming galaxies.
The study of nearby LAE samples has allowed the study of other
indicators that might be more difficult to obtain for distant galaxies
such as galaxy morphology, dust attenuation, neutral hydrogen contents and
ionization state. See \citep{Hayes15}, and references therein for a review.

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a 
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models
